### 2020-04-23 tbf.tex
last?

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/MTBF_GPUwise.pdf}
  \end{center}
  \caption{Distribution of device-level MTBFs due to DBE and OTB failures across all GPUs during the
entire lifetime of the machine. DBE and OTB events are separated for each GPU to distinguish between 
the failure pattern of each event type. Data includes both old and new batch of GPUs with the new ones 
mostly having MTBFs around or less than 3 years.}
  \label{fig:Device_MTBFs}
\end{figure}

@@

Apart from the center cluster, a considerable portion of GPUs also have a very 
low MTBF. This failure characteristic is mainly an artifact from
troubleshooting a period of increasing failures in mid to late 2016.
After a GPU experienced an OTB or a DBE a second reboot was attempted at
the same or possibly different location. Usually, but not always, a
second OTB or DBE was generated immediately or possibly after a short
time. When moved to a new location, this generates an artifact in our
data with an unusually short MTBF because we use the {\em insert} time as
a reference for the first failure on a relocated GPU. This drawback is
balanced by the advantage that this way we can discount out of service times
which were frequent particularly during early 2017 as can be seen in
Fig.~\ref{fig:sample_loc}.

On the other end of the spectrum, a noticeable portion of GPUs have very high
MTBFs and their failures are mostly DBEs. This is the population of the GPUs that see a continuous operation in the machine 
despite its various episodes and see a single DBE event during their lifetime.
Apart from this, the distribution of MTBF due to DBE events looks very similar to that due 
to OTB events. It can also be noted from Figure~\ref{fig:Device_MTBFs} that the number of recorded 
DBE events is significantly higher than the OTB events. This highlights the targeted replacement of GPUs 
with OTB events causing a substantial decrease in OTB events.

@@

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/MTBF_quaterly_sys.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF over the lifetime of the machine. System MTBF is calculated over 
three month periods to understand the various episodes of the machine. The three month periods are 
referred to as quarters, i.e., January through March is Q1, and so on. Most GPU replacements started taking 
place at the end of 2016-Q4 and were completed before 2018-Q1. DBE and OTB events are 
considered independently as well as together to represent failures occurring on the machine.}
  \label{fig:MTBF_sys}
\end{figure}

@@

When GPU replacements start to take place in late 
2016, it triggers a slight increase in MTBF. However, this change only lasts until 2018-Q1, when we see another 
downward trend of system MTBF. Incidentally, 2018-Q1 also marks the completion of all GPU replacements. 
So the upward trend noted in the period from 2016-Q4 to 2018-Q1 is
likely due to phased replacements, each time a portion of the machine 
being unavailable, thus having a smaller number of GPUs than the full
machine in operation. 
%\fix{need to verify how long the replacement took}
There is not definitive way to incorporate this unavailability of the
machine into MTBF analysis, unless we know how the down times were scheduled.
For example, the lowest MTBF obtained in 2016-Q4 is 2.7 hours, with the subsequent periods having the 
lowest MTBF of 5.9 hours. With system MTBF less than a day, even slight variations in MTBF make it 
difficult to reliably run applications despite using failure recovery approaches such as checkpoint restart, 
as discussed later on in Section~\ref{section:discussion}.

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/NumFailures_Quarterly_newOld.pdf}
  \end{center}
  \caption{The number of DBE and OTB failures observed over the lifetime of the machine.
A distinction is made between failures on old GPUs to highlight the number
of failures on the newer GPUs. The peak failures are seen in 2016-Q4 (813 failures), 
which marks the commencement of major replacement of GPUs in the machine.}
  \label{fig:NumFails_sys}
\end{figure}

We also separate the DBE and OTB failures in this analysis. After the
2017 replacement of many GPUs, there is a drastic increase in
mean-time-between OTB failures, which is also evident in a reduction of OTB failures in Figure~\ref{fig:NumFails_sys}.
However, the system MTBF is determined by the weakest link and here the occurrence of DBE events tends to dictate it.
Even though the replacements helped to increase the MTBF due to DBE events, the overall system 
reliability is dictated by the components with the most age in the
system. There is a re-emergence of an upward trend towards 
the end in DBE failures in Figure~\ref{fig:NumFails_sys}, which
appears to be due to older GPUs in the system.

\begin{figure}[bt]
  \begin{center}
    \includegraphics[width=\columnwidth]{figs/MTBF_quaterly_sys_NewOldALL.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF across hypothetical new and old partitions of the machine over time.
Results are presented from 2017-Q1 which marked the beginning of when a substantial number of new GPUs are in service.
DBE and OTB events are both considered as a failure for calculating the MTBF.
Results highlight the difference in reliability observed by jobs using the new GPUs as compared to old GPUs,
as well as the minute difference in MTBF measured across the old partition and the whole machine.}
  \label{fig:MTBF_sys_NewOld}
\end{figure}

>>>>

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_GPUwise.pdf}
  \end{center}
  \caption{Distribution of device-level MTBFs due to DBE and OTB failures across all GPUs during the
entire lifetime of the machine. DBE and OTB events are separated for each GPU to distinguish between 
the failure pattern of each event type. Data includes both old and new batch of GPUs with the new ones 
mostly having MTBFs around or less than 3 years.}
  \label{fig:Device_MTBFs}
\end{figure}

@@

Apart from the center cluster, many GPUs also have a very 
low MTBF. This failure characteristic is mainly an artifact from
troubleshooting a period of increasing failures in mid to late 2016.
After a GPU experienced an OTB or a DBE a second reboot was attempted at
the same or possibly different location. Usually, but not always, a
second OTB or DBE was generated immediately or possibly after a short
time. When moved to a new location, this generates an artifact in our
data with an unusually short MTBF because we use the {\em insert} time as
a reference for the first failure on a relocated GPU. This drawback is
balanced by the advantage that this way we can discount out of service times
which were frequent particularly during early 2017 as can be seen in
Fig.~\ref{fig:locview}.

On the other end of the spectrum, a noticeable portion of GPUs have very high
MTBFs and their failures are mostly DBEs. These are the GPUs that see continuous operation in the machine 
despite its various episodes and see a single DBE event during their lifetime.
Apart from this, the distribution of MTBF due to DBE events looks very similar to that due 
to OTB events. We also note in Figure~\ref{fig:Device_MTBFs} that the number of recorded 
DBE events is much higher than the OTB events. This highlights the targeted replacement of GPUs 
with OTB events causing a substantial decrease in OTB events.

@@

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_quaterly_sys.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF over the lifetime of the machine. System MTBF is calculated over 
three month periods to understand the various episodes of the machine. The three month periods are 
referred to as quarters, i.e., January through March is Q1, and so on. Most GPU replacements started taking 
place at the end of 2016-Q4 and were completed before 2018-Q1. DBE and OTB events are 
considered independently as well as together to represent failures occurring on the machine.}
  \label{fig:MTBF_sys}
\end{figure}

@@

When GPU replacements start to take place in late 
2016, it triggers a slight increase in MTBF. However, this change only lasts until 2018-Q1, when we see another 
downward trend of system MTBF. Incidentally, 2018-Q1 also marks the completion of all GPU replacements. 
So the upward trend noted in the period from 2016-Q4 to 2018-Q1 is
likely due to phased replacements, each time a portion of the machine 
being unavailable, thus having a smaller number of GPUs than the full
machine in operation. 
%\fix{need to verify how long the replacement took}
There is not definitive way to incorporate this unavailability of the
machine into MTBF analysis, unless we know how the down times were scheduled.
The lowest MTBF obtained in 2016-Q4 is 2.7 hours, with subsequent periods having the 
lowest MTBF of 5.9 hours. With system MTBF less than a day, even slight variations in MTBF make it 
difficult to reliably run applications despite using failure recovery approaches such as checkpoint restart, 
as discussed later on in Section~\ref{section:discussion}.

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/NumFailures_Quarterly_newOld.pdf}
  \end{center}
  \caption{The number of DBE and OTB failures observed over the lifetime of the machine.
A distinction is made between failures on old GPUs to highlight the number
of failures on the newer GPUs. The peak failures are seen in 2016-Q4 (813 failures), 
which marks the commencement of major replacement of GPUs in the machine.}
  \label{fig:NumFails_sys}
\end{figure}

\begin{figure}[bt]
  \begin{center}
    \includegraphics[trim={0 1em 0 1em},clip,width=\columnwidth]{figs/MTBF_quaterly_sys_NewOldALL.pdf}
  \end{center}
  \caption{Variation of system-wide MTBF across hypothetical new and
    old partitions of the machine after a substantial number of new GPUs
were put in service.
DBE and OTB events both determine the MTBF.
Results highlight the difference in reliability for jobs using the new GPUs as compared to old GPUs,
as well as now MTBF is driven by the weaker old partition.}
  \label{fig:MTBF_sys_NewOld}
\end{figure}
We also separate the DBE and OTB failures in this analysis. After the
2017 replacement of many GPUs, there is a drastic increase in
mean-time-between OTB failures, which is also evident in a reduction of OTB failures in Figure~\ref{fig:NumFails_sys}.
However, the system MTBF is determined by the weakest link and here the occurrence of DBE events tends to dictate it.
Even though the replacements helped to increase the MTBF due to DBE events, the overall system 
reliability is dictated by the components with the most age in the
system. There is a re-emergence of an upward trend towards 
the end in DBE failures in Figure~\ref{fig:NumFails_sys}, which
appears to be due to older GPUs in the system.
